---
title: "Eating Out"
author: "Rita Jarbanda"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE, warning=FALSE}
GSS <- readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods

```{r}
glimpse(mydata)
```

Looking at the data, we are comparing two categorical data types therefore we will use the CandP helper file for Cat~Cat. This will include a bar chart, the tidyverse barchart was used for its ability to show percentages vs ggplot2. Then we will look at numerical results using favstats and finally preform a chi squared test and a fisher exxact test via the fisherXY tool provided.

# Results

## Graphical Results

```{r include = TRUE, echo = FALSE}
barchartGC(~race + eatout,data=mydata, type="percent")
```

We can see from the results that the overall frequency of "white" is higher than both races however the difference from "black" is most pronounced. The "black" and "other" are more similar.

## Numerical Results

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
```

The white race is eating out almost 20% more likely than black race, once again we see that white eat out at a higher frequency than the other races.

## Inferential Results

```{r}
chisqtestGC(table1)
```






